Further Evidence of Modified Spin-down in Sun-like Stars:\\Pile-ups in the Temperature--Period Distribution

### 2022-02-02 src/ms.tex
JVS comments

We caution that the specific values of \rocrit found here are highly sensitive to shifts in the \teff scales between the models and observations, as well as the \teff scale of the models used to derive the \taucz relation. Therefore, while we find values of \rocritfinal are able to explain the various individual data sets, a value of \rocrit  $\approx$~2 may be compatible with all of the data sets if modest \teff systematics are present. Comparison of the long-period pile-ups as seen in the CKS and \lamostmcq samples support the notion that the LAMOST \teff scale is about 30--40~K cooler than the CKS scale (see also Appendix~\ref{app:teff}).

>>>>

We caution that the specific values of \rocrit found here are highly sensitive to shifts in the \teff scales between the models and observations, as well as the \teff scale of the models used to derive the \taucz relation. Therefore, while we find values of \rocritfinal are able to explain the various individual data sets, a value of \rocrit  $\approx$~2 is compatible with all of the data sets if modest \teff systematics are present. Comparison of the long-period pile-ups as seen in the CKS and \lamostmcq samples support the notion that the LAMOST \teff scale is about 30--40~K cooler than the CKS scale (see also Appendix~\ref{app:teff}).
